Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-11-26 _tex/manuscript.tex
Built site for gh-pages

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Section section~\ref{sec-data} presents a multi-centric dataset on
  lymph node involvement in 833 OPSCC patients, identifying key risk
  factors for contralateral lymph node involvement and outlining
  requirements for a bilateral model extension
  (section~\ref{sec-requirements}).
\item
  Section section~\ref{sec-ext-to-contra} introduces a bilateral HMM
  that incorporates primary tumor lateralization, T-category, and
  clinical involvement as risk factors for contralateral involvement.
  Model training and computational experiments are described in
  section~\ref{sec-methods}.
\item
  Section section~\ref{sec-results} demonstrates the model's ability to
  replicate observed contralateral lymph node involvement patterns and
  estimates occult disease risk for typical patients. Implications for
  volume-deescalated radiotherapy are discussed in
  section~\ref{sec-discussion}.
\end{enumerate}

@@

A straightforward approach to modeling contralateral lymphatic spread
would be to use two independent unilateral models, as described in
Section section~\ref{sec-unilateral}, with shared parameters such as the
distribution of diagnosis times or spread between LNLs (\(t_{vr}\)).
However, this method would fail to capture the correlation between
ipsilateral and contralateral involvement discussed in
section~\ref{sec-data-strat}, particularly the observed increase in
contralateral involvement with greater severity of ipsilateral spread.

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Section~\ref{sec-data} presents a multi-centric dataset on lymph node
  involvement in 833 OPSCC patients, identifying key risk factors for
  contralateral lymph node involvement and outlining requirements for a
  bilateral model extension (section~\ref{sec-requirements}).
\item
  Section~\ref{sec-ext-to-contra} introduces a bilateral HMM that
  incorporates primary tumor lateralization, T-category, and clinical
  involvement as risk factors for contralateral involvement. Model
  training and computational experiments are described in
  section~\ref{sec-methods}.
\item
  Section~\ref{sec-results} demonstrates the model's ability to
  replicate observed contralateral lymph node involvement patterns and
  estimates occult disease risk for typical patients. Implications for
  volume-deescalated radiotherapy are discussed in
  section~\ref{sec-discussion}.
\end{enumerate}

@@

A straightforward approach to modeling contralateral lymphatic spread
would be to use two independent unilateral models, as described in
section~\ref{sec-unilateral}, with shared parameters such as the
distribution of diagnosis times or spread between LNLs (\(t_{vr}\)).
However, this method would fail to capture the correlation between
ipsilateral and contralateral involvement discussed in
section~\ref{sec-data-strat}, particularly the observed increase in
contralateral involvement with greater severity of ipsilateral spread.
